### 2016-06-30 2nd_round_comments/DVCS-CAN-Meeting-Comments.tex
added the more answers to the comments

\section*{\centering{Summary of April 13, 2016 phone conference and requests from the NP-PWG review committee
M. Garcon, S. Kuhn and Zein-Eddine Meziani\\ 
to M. Hattawi and co-authors}}

@@

  \item Produce all 9 plots in right figure of slides 5 and 9 of \url{ 
     https://clasweb.jlab.org/rungroups/lowq/wiki/images/a/a0/ExcluCuts-CANeg6.pdf}   
     for a 2$\sigma$ and 1$\sigma$ cuts on missing $ep\gamma X$ M2.
    \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/all_sigmas_coh_exc_cuts.pdf}
    \caption{Coherent exclusivity distributions for the different cut 
    width on $e^{4}He\gamma X$ missing mass squared. }
    \label{fig:2d_delta_phi_MM2_InCoh}
    \end{figure}                                                                  
    \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/all_sigmas_incoh_exc_cuts.pdf}
    \caption{ Incoherent exclusivity distributions for the different cut  
    width on $ep\gamma X$ missing mass squared.}
    \label{fig:2d_delta_phi_MM2_InCoh}
    \end{figure}

    \end{enumerate}
\item (optionally) In the incoherent case, extract ALU with 2 variations of the 
   ep missing M2 right cut, moving it tighter to the left (e.g.  1 and 0.75 
   GeV2).  (also see the evolution of the other distributions when doing so).
\end{enumerate}

>>>>

\section*{\centering{Summary of April 13, 2016 phone conference and requests from the NP-PWG review committee
M. Garcon, S. Kuhn and Zein-Eddine Meziani\\ to M. Hattawy and co-authors}}

@@

  \item Produce all 9 plots in right figure of slides 5 and 9 of \url{ 
     https://clasweb.jlab.org/rungroups/lowq/wiki/images/a/a0/ExcluCuts-CANeg6.pdf}   
     for a 2$\sigma$ and 1$\sigma$ cuts on missing $ep\gamma X$ M2.
    \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/all_sigmas_coh_exc_cuts.pdf}
    \caption{Coherent exclusivity distributions for the different cut 
    width on $e^{4}He\gamma X$ missing mass squared. }
    \label{fig:2d_delta_phi_MM2_InCoh}
    \end{figure}                                                                  
    \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/all_sigmas_incoh_exc_cuts.pdf}
    \caption{ Incoherent exclusivity distributions for the different cuts on 
    $ep\gamma X$ missing mass squared.}
    \label{fig:2d_delta_phi_MM2_InCoh}
    \end{figure}

    \end{enumerate}
\item (optionally) In the incoherent case, extract ALU with 2 variations of the 
   ep missing M2 right cut, moving it tighter to the left (e.g.  1 and 0.75 
   GeV2).  (also see the evolution of the other distributions when doing so).

   \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/BSA_incoherent_epMM.png}
    \caption{ The integrated, over $Q^{2}$, $x_{B}$, and $-t$, incoherent 
    beam-spin asymmetries as a function of $\phi$ for the different cuts on 
 $epX$ missing mass squared.}
    \label{fig:BSA_incoherent_epMM}
    \end{figure}

    \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/epMM2_incoh_exc_cuts.pdf}
    \caption{ Incoherent exclusivity distributions for the different cuts on 
    $epX$ missing mass squared.}
    \label{fig:epMM2_incoh_exc_cuts}
    \end{figure}

\end{enumerate}
